\Large {\bf Protocol-Guided Analysis of Post-silicon Traces Under Limited Observability}

### 2016-01-03 paper.tex
removed bookmarks
Added an option in order to disable bookmarks in the compiled PDF.

\documentclass[conference]{IEEEtran}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mybeamer}
%\usepackage{draftwatermark}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

@@

For this model, we consider the flow specifications
describing the cache coherence protocols supported in
GEM5\footnote{The GEM5 cache coherence protocols can be
  found at
  \url{http://www.gem5.org/docs/html/gem5MemorySystem.html}.}
that is used to build the model in Fig~\ref{SoC}.  These
flow specifications describe data/instruction read
operations and data write operations initiated from CPUs.
Three such flows describe the cache coherent protocols for
each CPU.  Since there are two CPUs, there are six flows in
the model.

>>>>

\documentclass[conference]{IEEEtran}

\PassOptionsToPackage{bookmarks={false}}{hyperref}

\usepackage{pifont}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mybeamer}
%\usepackage{draftwatermark}
%\usepackage[]{hyperref}
%\hypersetup{
%    bookmarks    = false,            % show bookmarks bar?
%    colorlinks=true,
%    linkcolor=blue,
%    filecolor=magenta,      
%    urlcolor=cyan,
%}
%

@@

For this model, we consider the flow specifications
describing the cache coherence protocols supported in
GEM5 that is used to build the model in Fig~\ref{SoC}.
The GEM5 cache coherence protocols can be found at~\cite{gem5}.
These flow specifications describe data/instruction read
operations and data write operations initiated from CPUs.
Three such flows describe the cache coherent protocols for
each CPU.  Since there are two CPUs, there are six flows in
the model.
